Holomorphic field theories and higher algebra

### 2022-12-06 draft.tex
b model

\begin{dfn}
Fix a positive integer $F$, for flavor, and fix integers $N$ and $\check{N}$ such that $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
\begin{itemize}
\item
The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors and {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
\item
The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ which take values in $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{\nu}$ for the partner field to $\check{\mu}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\end{itemize}
\end{dfn}

@@

A beautiful maneuver used in physics is compactification:
given a field theory $\cT$ in $n$ dimensions, one takes an $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.
We have already worked with a factorization algebra version of these maneuvers: 
pushing forward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
For a holomorphic factorization algebra $\cF$, the pushforward $\rho_* \cF$ is locally constant on $\RR_{\geq 0}^2 \cong \RR^2$, and hence it encodes an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would mean.

\begin{lem}
For a holomorphic QCD theory $\cT(F,N)$, this compactification is a Landau-Ginzburg B-model~$\cT(F,N)_2$.
\owen{Not sure what's the best way to characterize which one we get.}
\end{lem}

@@

\begin{conj}
There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
the compactifications of the electric and magnetic holomorphic QCD theories.
\end{conj}

>>>>

\begin{dfn}
Fix a positive integer $F$, for flavor, and fix integers $N$ and $\check{N}$ such that $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
\begin{itemize}
\item
The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors and {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.
\item
The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{\mu}$ which take values in $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{\nu}$ for the partner field to $\check{\mu}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is 
\beqn\label{eqn:checkW}
\check{W} =  \Tr(\check{Q}^\dag \check{\mu}  \check{Q})
\eeqn
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\end{itemize}
\end{dfn}

@@

A standard maneuver used in physics is compactification:
given a field theory $\cT$ in $n$ dimensions, one takes compact $n-k$-manifold $N$ and produces a field theory $\cT_N$ in $k$ dimensions by studying $\cT$ on manifolds of the form $N \times \Sigma$, where $\Sigma$ is $k$-dimensional.
One then considers the push forward of the theory along the obvious map $N \times \Sigma \to \Sigma$, to obtain an effective theory along $\Sigma$.
A close cousin is dimensional reduction, where one restricts to solutions of the classical field theory that are constant along $N$.

We consider a holomorphic theory defined on $\C^\times \times \C^\times$ and the pushforward along the map $\rho: \CC^\times \times \CC^\times \to \RR_{>0} \times \RR_{>0}$ that sends $(z_1,z_2)$ to $(|z_1|, |z_2|)$.
In other words, this is the $T^2$ compactification of the holomorphic theory.
For a holomorphic factorization algebra $\cF$, one can extract from the pushforward $\rho_* \cF$ a locally constant factorization algebra on $\RR_{> 0}^2 \cong \RR^2$, hence an $E_2$-algebra.
We now apply this result in the context of holomorphic QCD and see what Seiberg duality would imply.

Let's first consider the electric side which breaks up into holomorphic BF theory coupled to a complex two-dimensional $\beta\gamma$ system.
The $T^2$ compactification of the $\beta\gamma$ system with target $\C^{NF}$ is the topological B-model theory whose target is the formal double loop space $L^2\C^{NF}$. 
This is the space whose algebra of functions is $\cO(\C^{NF}) ((z))((w))$ where $z,w$ are formal loop parameters which we imagine as describing the winding of the two circles we have compactified. 
The dimensional reduction simply picks out the constant modes along each circle, so we find a linear topological B-model with target $\C^{NF}$.
Similarly, the dimensional reduction of holomorphic BF theory is topological BF theory (which is a stacky version of the B-model whose target is $B GL(N)$).
In sum, the dimensional reduction of the electric holomorphic QCD is the topological B-model whose target is the stack $\C^{NF} / GL(N)$.
As a derived mapping space, this model is given by
\beqn
{\rm Map}\left(\RR^2, T^*[1] \C^{NF} / GL(N)\right) .
\eeqn
The factorization algebra of observables obtained from reduction encodes the $E_2$ algebra of (holomorphic) polyvector fields on the stack $\C^{NF} / GL(N)$.

On the magnetic side the reduction is similar, except this time we must take into account the superpotential. 
What results is a Landau--Ginzburg B-model whose target is the stack
\beqn
\C^{(F-N)F} / GL(F-N) \times \C^{F^2} .
\eeqn
The first factor comes from the reduction of the dual quarks coupled to the dual gauge theory, and the second factor comes from the reduction of the mesons. 
The potential of the Landau--Ginzburg model is given by the same expression $\check{W}$ as in \eqref{eqn:checkW}.

@@

\begin{conj}
There is an equivalence of $E_2$ algebras between:
\begin{itemize} 
\item (electric) the $E_2$ algebra of polyvector fields on the stack $\C^{NF} / GL(N)$.
\item (magnetic) the $E_2$ algebra which results from deforming the $E_2$ algebra of polyvector fields on the stack $\C^{(F-N)F} / GL(F-N) \times \C^{F^2}$ by the differential $\{\check{W},-\}$ where $\{-,-\}$ is the Schouten bracket.
\end{itemize}
\end{conj}

%\begin{conj}
%There is an equivalence between $\cT_{\sfE}(F,N)_2$ and $\cT_{\sfM}(F,N)_2$, 
%the compactifications of the electric and magnetic holomorphic QCD theories.
%\end{conj}
